Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2020-11-25 numerics_paper/version2/numerical_chj.tex
Remove boldface characters.
tmp branch to update numerical results

\newcommand{\W}{{\mathcal W}}
\newcommand{\A}{{\mathcal A}}
\newcommand{\apdq}{\A^+ \!\!{\Delta} Q}
\newcommand{\amdq}{\A^- \!\!{\Delta} Q}
\newcommand{\Ft}{\tilde{F}}
\newcommand{\imh}{{i-1/2}}
\newcommand{\iph}{{i+1/2}}
\newcommand{\bff}{{\bf f}}
\newcommand{\bfr}{{\bf r}}
\newcommand{\bfF}{{\bf F}}
\newcommand{\bfu}{{\bf u}}
\newcommand{\bfv}{{\bf v}}
\newcommand{\bfq}{{\bf q}}
\newcommand{\bfx}{{\bf x}}
\newcommand{\sgn}{{\rm sgn}}
\newcommand{\Rus}{{\rm Rus}}
\newcommand{\Roe}{{\rm Roe}}

@@

\begin{table}[!ht]\scriptsize
  \begin{center}
    \begin{tabular}{||c||c|c||c|c||c|c||c|c||} \hline
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver}
      &\multicolumn{2}{c||}{Roe's with $\lambda_{i\pm 1/2}^{\min}$} \\ \cline{2-9}
      $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate \\ \hline
      1/50   & 6.21E-04 &  --  & 6.95E-04 &   -- & 5.10E-04 &  --  & 5.95E-04 & --   \\
      1/100  & 4.70E-04 & 0.40 & 5.27E-04 & 0.40 & 3.53E-04 & 0.52 & 4.06E-04 & 0.55 \\
      1/200  & 3.91E-04 & 0.26 & 3.88E-04 & 0.44 & 2.38E-04 & 0.56 & 2.83E-04 & 0.52 \\
      1/400  & 3.16E-04 & 0.30 & 2.64E-04 & 0.55 & 1.51E-04 & 0.65 & 1.89E-04 & 0.58 \\
      1/800  & 2.35E-04 & 0.42 & 1.67E-04 & 0.66 & 9.43E-05 & 0.68 & 1.20E-04 & 0.65 \\
      1/1600 & 2.00E-04 & 0.23 & 1.01E-04 & 0.72 & 5.70E-05 & 0.72 & 7.42E-05 & 0.68 \\ \hline
    \end{tabular}
    \caption{Grid convergence study for the dam break problem over a dry bed
      using method \eqref{first-order_via_fluct} with different Riemann solvers.\label{table:rp_dry_bed}}
  \end{center}
\end{table}

@@

\begin{table}[!ht]\scriptsize
  \begin{center}
    \begin{tabular}{||c||c|c||c|c||c|c||} \hline
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver} \\ \cline{2-7}
      $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate \\ \hline
      1/50   & 4.22E-04 &  --  & 5.73E-04 &  --  & 4.34E-04 & --   \\
      1/100  & 2.00E-04 & 1.07 & 3.35E-04 & 0.78 & 2.08E-04 & 1.05 \\
      1/200  & 1.11E-04 & 0.85 & 2.01E-04 & 0.74 & 1.13E-04 & 0.88 \\
      1/400  & 5.05E-05 & 1.13 & 1.18E-04 & 0.77 & 5.26E-05 & 1.10 \\
      1/800  & 2.60E-05 & 0.95 & 7.08E-05 & 0.74 & 2.73E-05 & 0.94 \\
      1/1600 & 1.29E-05 & 1.01 & 3.79E-05 & 0.90 & 1.32E-05 & 1.04 \\ \hline
    \end{tabular}
    \caption{Grid convergence study for the dam break problem over a wet bed
      using method \eqref{second-order_via_fluct} with different Riemann solvers.\label{table:rp_wet_bed}}
  \end{center}
\end{table}

\subsection{The circular hydraulic jump in one-dimension}\label{sec:1D_chj}
In this section we consider for the first time a CHJ. We start with a one-dimensional problem
embedded into the two-dimensional domain $\Omega=(0.1,1)\times(0,0.1)$.
A semi-analytical solution at steady state is available as described in \S \ref{sec:steady_chj};
therefore, we can perform a convergence test.
We consider the initial condition $h(x,t=0)=0.1$, $hu(x,t=0)=0$ and $hv(x,t=0)=0$.
At the left boundary, we impose $h(0.1,t)=0.3$, $hu(0.1,t)=0.225$ and $hv(0.1,t)=0$.
At the right boundary we impose $h(1,t)=0.37387387318873766$, $hu(1,t)=\beta/h(1,t)$ and $hv(1,t)=0$ where $\beta=0.0225$.
The values on the right boundary are chosen so that the CHJ is located at $x=0.3$, as described in \S \ref{sec:formation}.
%
In the first row of Figure \ref{fig:rp_wet_bed}, we show (slices of) the solution (at $y=0.05$)
at different times using the second-order method \eqref{second-order_via_fluct} with Roe's, Rusanov's and the blended Riemann solvers.
In the second row of the same figure, we plot $\theta_i$ \eqref{Ri}, which is a (normalized) measurement of the
entropy residual. Note that $\theta_i$ accurately locates the shocks and is (nearly) zero in smooth regions.
In Table \ref{table:chj_1D}, we summarize the results of a convergence study.
We remark that the convergence with Roe's solver is erratic.
Moreover, for the finer grids, the solution appears to become worse.
Using Rusanov's and the blended Riemann solvers delivers cleaner convergence rates.
In \cite[\S 5]{kemm2018heuristical} and \cite{bader2014carbuncle}, the authors consider one-dimensional problems embedded into
two-dimensional domains and observe different instabilities for the
Euler and the shallow water equations, respectively.
The authors attributed the problem to a manifestation of the carbuncle instability
that lead to an unstable location of the steady shock with certain Riemann solvers, including Roe's solver.

\begin{figure}[!h]
  {\scriptsize
    \includegraphics[scale=0.29]{figures/chj_1D_t0p5.png}
    \qquad
    \includegraphics[scale=0.29]{figures/chj_1D_t1p3.png}
    \qquad
    \includegraphics[scale=0.29]{figures/chj_1D_t10p0.png}

    \vspace{15pt}
    \includegraphics[scale=0.29]{figures/chj_1D_Ri_t0p5.png}
    \qquad
    \includegraphics[scale=0.29]{figures/chj_1D_Ri_t1p3.png}
    \qquad
    \includegraphics[scale=0.29]{figures/chj_1D_Ri_t10p0.png}
  }
  \caption{
    One-dimensional CHJ using method \eqref{second-order_via_fluct} with
    (cyan) Roe's, (red) Rusanov's and (blue) the blended Riemann solvers.
    In the second row we plot $\theta_i$, which is given by \eqref{Ri}.
    In all simulations we consider $\Delta x=1/400$.
    \label{fig:1D_chj}}
\end{figure}

\begin{table}[!ht]\scriptsize
  \begin{center}
    \begin{tabular}{||c||c|c||c|c||c|c||} \hline
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver} \\ \cline{2-7}
      $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate \\ \hline
      1/50  & 1.56E-04 &  --   & 8.80E-04 &  --  & 3.56E-04 &  --  \\
      1/100 & 1.06E-04 & 0.55  & 5.09E-04 & 0.79 & 1.95E-04 & 0.86 \\
      1/200 & 7.77E-05 & 0.45  & 2.96E-04 & 0.78 & 1.07E-04 & 0.87 \\
      1/400 & 7.50E-06 & 3.37  & 1.49E-04 & 0.99 & 3.68E-05 & 1.53 \\
      1/800 & 9.07E-06 & -0.27 & 7.98E-05 & 0.90 & 1.67E-05 & 1.14 \\ \hline
    \end{tabular}
    \caption{Grid convergence study for the one-dimensional CHJ at $t=10$
      using method \eqref{second-order_via_fluct} with different Riemann solvers.\label{table:chj_1D}}
  \end{center}
\end{table}

\subsection{Steady outflow}\label{sec:steady_outflow}
Let us consider a problem similar to that in the previous section, but with an outflow boundary condition.
That is, we consider the one-dimensional domain $\Omega=(0.1,1)$, the initial condition
$h(x,t=0)=0.1$, $hu(x,t=0)=0$, the left boundary condition $h(0.1,t)=0.3$, $hu(0.1,t)=0.75$,
and set the right boundary condition to outflow.
We refer to \cite[\S 21.8.5]{leveque2002finite} for details about the outflow boundary condition.
If the flow is supercritical ($|F|>1$ where $F$ is the Froude number), the exact solution converges to a
steady state profile given by the solution of \eqref{steady}.
Depending on the initial condition, shocks might develop before the steady state is reached.
Nevertheless, the steady state profile is smooth.
In Figure \ref{fig:steady_outflow}, we show the solution and $\theta_i$ at different times using
the second-order method \eqref{second-order_via_fluct}
with Roe's, Rusanov's and the blended Riemann solvers.
Additionally, in Table \ref{table:steady_outflow}, we summarize the results of a convergence study
based on methods \eqref{first-order_via_fluct} and
\eqref{second-order_via_fluct}, using the same Riemann solvers.

@@

\begin{table}[!ht]\scriptsize
  \begin{center}
    \begin{tabular}{||c||c|c||c|c||c|c||c|c||c|c||c|c||} \hline
      & \multicolumn{6}{c||}{First-order method \eqref{first-order_via_fluct}}
      & \multicolumn{6}{c||}{Second-order method \eqref{second-order_via_fluct}} \\ \cline{2-13}
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver}
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver}
      \\ \cline{2-13}
      $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate\\ \hline
      1/50   & 2.16E-4 &  --  & 9.97E-4 &   -- & 2.20E-4 & --   & 4.13E-5 &   -- & 7.32E-4 &  --  & 4.97E-5 & --   \\
      1/100  & 1.14E-4 & 0.92 & 6.38E-4 & 0.64 & 1.16E-4 & 0.92 & 1.47E-5 & 1.48 & 4.43E-4 & 0.73 & 1.89E-5 & 1.39 \\
      1/200  & 5.86E-5 & 0.95 & 3.88E-4 & 0.72 & 5.93E-5 & 0.96 & 4.81E-6 & 1.61 & 2.57E-4 & 0.79 & 6.36E-6 & 1.57 \\
      1/400  & 2.98E-5 & 0.97 & 2.26E-4 & 0.78 & 3.00E-5 & 0.98 & 1.42E-6 & 1.76 & 1.44E-4 & 0.83 & 1.92E-6 & 1.72 \\
      1/800  & 1.50E-5 & 0.98 & 1.27E-4 & 0.83 & 1.51E-5 & 0.99 & 4.16E-7 & 1.76 & 7.81E-5 & 0.88 & 5.61E-7 & 1.77 \\
      1/1600 & 7.53E-6 & 0.99 & 6.90E-5 & 0.88 & 7.55E-6 & 0.99 & 1.14E-7 & 1.86 & 4.12E-5 & 0.92 & 1.54E-7 & 1.86 \\ \hline
    \end{tabular}
    \caption{Grid convergence study for the steady outflow problem
      using methods \eqref{first-order_via_fluct} and \eqref{second-order_via_fluct}
      with different Riemann solvers.\label{table:steady_outflow}}
  \end{center}
\end{table}

%\clearpage
\subsection{Steady shock around a cylinder}\label{sec:bow_shock}
\subsection{The circular hydraulic jump in two dimensions}\label{sec:2D_chj}
%We consider two regimes. In the first regime, the physical instabilities are mild.
%By increasing the strength of the jump and other parameters, we consider a second
%and more strongly unstable regime. In both cases, we generate the CHJ as described in
%Section XX; that is, we impose supersonic inflow boundary conditions for the jet and
%subsonic outflow boundary conditions.

%We consider two types of domain and two corresponding computational grids.
%The two types of domains are two-dimensional squares and circular domains.
%For both cases we use structured grids. See an example of these domains and grids in Figures XX and XX,
%respectively.

>>>>

\newcommand{\W}{{\mathcal W}}
\newcommand{\A}{{\mathcal A}}
\newcommand{\apdq}{\A^+ \!\!{\Delta} Q}
\newcommand{\amdq}{\A^- \!\!{\Delta} Q}
\newcommand{\Ft}{\tilde{F}}
\newcommand{\imh}{{i-1/2}}
\newcommand{\iph}{{i+1/2}}
\newcommand{\bff}{{\bf f}}
\newcommand{\bfr}{{\bf r}}
\newcommand{\bfF}{{\bf F}}
\newcommand{\bfu}{{\bf u}}
\newcommand{\bfv}{{\bf v}}
\newcommand{\bfq}{{\bf q}}
\newcommand{\bfx}{{\bf x}}
\newcommand{\sgn}{{\rm sgn}}
\newcommand{\Rus}{{\rm Rus}}
\newcommand{\Roe}{{\rm Roe}}
\newcommand{\Fr}{{\rm Fr}}

@@

\begin{table}[!ht]\scriptsize
  \begin{center}
    \begin{tabular}{||c||c|c||c|c||c|c||c|c||} \hline
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver}
      &\multicolumn{2}{c||}{Roe's with $\lambda_{i\pm 1/2}^{\min}$} \\ \cline{2-9}
      $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate \\ \hline
      1/50   & 6.21E-04 &  --  & 6.95E-04 &   -- & 5.08E-04 & --   & 5.95E-04 & --   \\
      1/100  & 4.70E-04 & 0.40 & 5.27E-04 & 0.40 & 3.39E-04 & 0.58 & 4.06E-04 & 0.55 \\
      1/200  & 3.91E-04 & 0.26 & 3.88E-04 & 0.44 & 2.30E-04 & 0.56 & 2.83E-04 & 0.52 \\
      1/400  & 3.16E-04 & 0.30 & 2.64E-04 & 0.55 & 1.49E-04 & 0.62 & 1.89E-04 & 0.58 \\
      1/800  & 2.35E-04 & 0.42 & 1.67E-04 & 0.66 & 9.24E-05 & 0.68 & 1.20E-04 & 0.65 \\
      1/1600 & 2.00E-04 & 0.23 & 1.01E-04 & 0.72 & 5.66E-05 & 0.70 & 7.42E-05 & 0.68 \\ \hline
    \end{tabular}
    \caption{Grid convergence study for the dam break problem over a dry bed
      using method \eqref{first-order_via_fluct} with different Riemann solvers.\label{table:rp_dry_bed}}
  \end{center}
\end{table}

@@

\begin{table}[!ht]\scriptsize
  \begin{center}
    \begin{tabular}{||c||c|c||c|c||c|c||} \hline
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver} \\ \cline{2-7}
      $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate \\ \hline
      1/50   & 4.22E-04 &  --  & 5.73E-04 &  --  & 4.24E-04 &  --  \\ 
      1/100  & 2.00E-04 & 1.07 & 3.35E-04 & 0.78 & 1.99E-04 & 1.08 \\
      1/200  & 1.11E-04 & 0.85 & 2.01E-04 & 0.74 & 1.10E-04 & 0.84 \\
      1/400  & 5.05E-05 & 1.13 & 1.18E-04 & 0.77 & 5.07E-05 & 1.12 \\
      1/800  & 2.60E-05 & 0.95 & 7.08E-05 & 0.74 & 2.61E-05 & 0.95 \\
      1/1600 & 1.29E-05 & 1.01 & 3.79E-05 & 0.90 & 1.29E-05 & 1.01 \\ \hline
    \end{tabular}
    \caption{Grid convergence study for the dam break problem over a wet bed
      using method \eqref{second-order_via_fluct} with different Riemann solvers.\label{table:rp_wet_bed}}
  \end{center}
\end{table}

%% \subsection{The circular hydraulic jump in one-dimension}\label{sec:1D_chj}
%% In this section we consider for the first time a CHJ. We start with a one-dimensional problem
%% embedded into the two-dimensional domain $\Omega=(0.1,1)\times(0,0.1)$.
%% A semi-analytical solution at steady state is available as described in \S \ref{sec:steady_chj};
%% therefore, we can perform a convergence test.
%% We consider the initial condition $h(x,t=0)=0.1$, $hu(x,t=0)=0$ and $hv(x,t=0)=0$.
%% At the left boundary, we impose $h(0.1,t)=0.3$, $hu(0.1,t)=0.225$ and $hv(0.1,t)=0$.
%% At the right boundary we impose $h(1,t)=0.37387387318873766$, $hu(1,t)=\beta/h(1,t)$ and $hv(1,t)=0$ where $\beta=0.0225$.
%% The values on the right boundary are chosen so that the CHJ is located at $x=0.3$, as described in \S \ref{sec:formation}.
%% %
%% In the first row of Figure \ref{fig:rp_wet_bed}, we show (slices of) the solution (at $y=0.05$)
%% at different times using the second-order method \eqref{second-order_via_fluct} with Roe's, Rusanov's and the blended Riemann solvers.
%% In the second row of the same figure, we plot $\theta_i$ \eqref{Ri}, which is a (normalized) measurement of the
%% entropy residual. Note that $\theta_i$ accurately locates the shocks and is (nearly) zero in smooth regions.
%% In Table \ref{table:chj_1D}, we summarize the results of a convergence study.
%% We remark that the convergence with Roe's solver is erratic.
%% Moreover, for the finer grids, the solution appears to become worse.
%% Using Rusanov's and the blended Riemann solvers delivers cleaner convergence rates.
%% In \cite[\S 5]{kemm2018heuristical} and \cite{bader2014carbuncle}, the authors consider one-dimensional problems embedded into
%% two-dimensional domains and observe different instabilities for the
%% Euler and the shallow water equations, respectively.
%% The authors attributed the problem to a manifestation of the carbuncle instability
%% that lead to an unstable location of the steady shock with certain Riemann solvers, including Roe's solver.

%% \begin{figure}[!h]
%%   {\scriptsize
%%     \includegraphics[scale=0.29]{figures/chj_1D_t0p5.png}
%%     \qquad
%%     \includegraphics[scale=0.29]{figures/chj_1D_t1p3.png}
%%     \qquad
%%     \includegraphics[scale=0.29]{figures/chj_1D_t10p0.png}

%%     \vspace{15pt}
%%     \includegraphics[scale=0.29]{figures/chj_1D_Ri_t0p5.png}
%%     \qquad
%%     \includegraphics[scale=0.29]{figures/chj_1D_Ri_t1p3.png}
%%     \qquad
%%     \includegraphics[scale=0.29]{figures/chj_1D_Ri_t10p0.png}
%%   }
%%   \caption{
%%     One-dimensional CHJ using method \eqref{second-order_via_fluct} with
%%     (cyan) Roe's, (red) Rusanov's and (blue) the blended Riemann solvers.
%%     In the second row we plot $\theta_i$, which is given by \eqref{Ri}.
%%     In all simulations we consider $\Delta x=1/400$.
%%     \label{fig:1D_chj}}
%% \end{figure}

%% \begin{table}[!ht]\scriptsize
%%   \begin{center}
%%     \begin{tabular}{||c||c|c||c|c||c|c||} \hline
%%       & \multicolumn{2}{c||}{Roe's solver}
%%       &\multicolumn{2}{c||}{Rusanov's solver}
%%       &\multicolumn{2}{c||}{Blended solver} \\ \cline{2-7}
%%       $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate \\ \hline
%%       1/50  & 1.56E-04 &  --   & 8.80E-04 &  --  & 2.48E-04 & -- \\
%%       1/100 & 1.06E-04 & 0.55  & 5.09E-04 & 0.79 & 1.70E-04 & 0.54 \\
%%       1/200 & 7.77E-05 & 0.45  & 2.96E-04 & 0.78 & 9.24E-05 & 0.87 \\
%%       1/400 & 7.50E-06 & 3.37  & 1.49E-04 & 0.99 & 1.70E-05 & 2.44 \\
%%       1/800 & 9.07E-06 & -0.27 & 7.98E-05 & 0.90 & 1.28E-05 & 0.40 \\ \hline
%%     \end{tabular}
%%     \caption{Grid convergence study for the one-dimensional CHJ at $t=10$
%%       using method \eqref{second-order_via_fluct} with different Riemann solvers.\label{table:chj_1D}}
%%   \end{center}
%% \end{table}

\subsection{Steady outflow}\label{sec:steady_outflow}
Let us consider a one-dimensional problem with a constant inflow and a steady outflow.
The domain is given by $\Omega=(0.1,1)$, the initial condition is
$h(x,t=0)=0.1$, $hu(x,t=0)=0$, the left boundary condition is $h(0.1,t)=0.3$, $hu(0.1,t)=0.75$,
and the right boundary condition is set to outflow.
We refer to \cite[\S 21.8.5]{leveque2002finite} for details about the outflow boundary condition.
If the flow is supercritical ($|\Fr|>1$ where $\Fr$ is the Froude number), the exact solution converges to a
steady state profile given by the solution of \eqref{steady}.
Depending on the initial condition, shocks might develop before the steady state is reached.
Nevertheless, the steady state profile is smooth.
In Figure \ref{fig:steady_outflow}, we show the solution and $\theta_i$ at different times using
the second-order method \eqref{second-order_via_fluct}
with Roe's, Rusanov's and the blended Riemann solvers.
Additionally, in Table \ref{table:steady_outflow}, we summarize the results of a convergence study
based on methods \eqref{first-order_via_fluct} and
\eqref{second-order_via_fluct}, using the same Riemann solvers.

@@

\begin{table}[!ht]\scriptsize
  \begin{center}
    \begin{tabular}{||c||c|c||c|c||c|c||c|c||c|c||c|c||} \hline
      & \multicolumn{6}{c||}{First-order method \eqref{first-order_via_fluct}}
      & \multicolumn{6}{c||}{Second-order method \eqref{second-order_via_fluct}} \\ \cline{2-13}
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver}
      & \multicolumn{2}{c||}{Roe's solver}
      &\multicolumn{2}{c||}{Rusanov's solver}
      &\multicolumn{2}{c||}{Blended solver}
      \\ \cline{2-13}
      $\Delta x$ & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate & $E_1$ & rate\\ \hline
      1/50   & 2.16E-4 &  --  & 9.97E-4 &   -- & 2.16E-4 & --   & 4.13E-5 &   -- & 7.32E-4 &  --  & 4.15E-5 & --   \\
      1/100  & 1.14E-4 & 0.92 & 6.38E-4 & 0.64 & 1.14E-4 & 0.92 & 1.47E-5 & 1.48 & 4.43E-4 & 0.73 & 1.48E-5 & 1.48 \\
      1/200  & 5.86E-5 & 0.95 & 3.88E-4 & 0.72 & 5.87E-5 & 0.95 & 4.81E-6 & 1.61 & 2.57E-4 & 0.79 & 4.83E-6 & 1.61 \\
      1/400  & 2.98E-5 & 0.97 & 2.26E-4 & 0.78 & 2.98E-5 & 0.97 & 1.42E-6 & 1.76 & 1.44E-4 & 0.83 & 1.42E-6 & 1.76 \\
      1/800  & 1.50E-5 & 0.98 & 1.27E-4 & 0.83 & 1.50E-5 & 0.98 & 4.16E-7 & 1.76 & 7.81E-5 & 0.88 & 4.18E-7 & 1.76 \\
      1/1600 & 7.53E-6 & 0.99 & 6.90E-5 & 0.88 & 7.53E-6 & 0.99 & 1.14E-7 & 1.86 & 4.12E-5 & 0.92 & 1.15E-7 & 1.86 \\ \hline
    \end{tabular}
    \caption{Grid convergence study for the steady outflow problem
      using methods \eqref{first-order_via_fluct} and \eqref{second-order_via_fluct}
      with different Riemann solvers.\label{table:steady_outflow}}
  \end{center}
\end{table}

\subsection{Steady shock around a cylinder}\label{sec:bow_shock}

\subsection{The circular hydraulic jump in two dimensions}\label{sec:2D_chj}
Let us finally consider the numerical experiments for the CHJ in two-dimensions.
The domain is given by the annulus $\Omega=\{(x,y)~|~ 0.1\leq\sqrt{x^2+y^2}\leq 1\}$.
The computational mesh is a logically quadrilateral mesh, see Figure \ref{fig:mesh_chj}.
In all the experiments in this section, the mesh consists of $10^6$ cells. 
Let
\begin{align*}
  \partial\Omega_I:=\{(x,y)\in\Omega ~|~ \sqrt{x^2+y^2}=0.1\}, \qquad \mbox{ and } \qquad
  \partial\Omega_o:=\{(x,y)\in\Omega ~|~ \sqrt{x^2+y^2}=1\},
\end{align*}
denote the inflow and outflow boundaries, respectively. 
The boundary conditions are 
\begin{subequations}\label{bcs_chj}
  \begin{align}
  h(x,y,t)=h_I, \quad
  u(x,y,t)=|\bfu_I| \left(\frac{x}{r_I}\right), \quad
  v(x,y,t)=|\bfu_I| \left(\frac{y}{r_I}\right), \qquad \forall (x,y)\in\partial\Omega_I, \\
  %
  h(x,y,t)=h_o, \quad 
  u(x,y,t)= \frac{\beta }{r_o h}\left(\frac{x}{r_o}\right), \quad
  v(x,y,t)= \frac{\beta }{r_o h}\left(\frac{y}{r_o}\right), \qquad \forall (x,y)\in\partial\Omega_o, \label{bcs_chj_outflow}
  \end{align}
\end{subequations}
where $h_I=0.3$, $r_I=0.1$, $r_o=1$ and $\beta=r_Ih_I|\bfu_I|$.
We choose $|\bfu_I|$ and $h_o$ to generate a radially symmetric shock at $r_s:=\sqrt{x^2+y^2}=0.3$, as described in \S \ref{sec:steady_chj}.
By selecting the boundary conditions $|\bfu_I|$ and $h_o$ we can move through different regimes.
In particular, we consider two cases.
For the first case, the Froude number at the inflow boundary is $\Fr\approx 1.3693$.
In this case, the CHJ appears to be nearly stable.
However, using Roe's solver leads to the formation of carbuncle instabilities.
%
The second regime is a more aggresive regime with a Froude number of $\Fr\approx 27.3861$ at the inflow boundary. 
In this regime, using Roe's solver also leads to carbuncle instabilities. In addition, 
due to the large Froude number, random perturbations might trigger physical instabilities. 
If the random perturbations model or mimic real disturbances in a physical experiment, it is then
desirable to properly simulate the unstable behavior of the flow without developing carbuncle instabilities. 
Therefore, the numerical method must introduce a carbuncle fix without dissipating important features of the
solution that could lead to physical instabilities. 
For this reason, we believe this problem is more challenging than the standard bow shock problem.

\begin{figure}[!h]
  \centering 
  \includegraphics[scale=0.15]{figures/mesh.png}
  \caption{
    Example of a grid for the problem with the two-dimensional CHJ.
    \label{fig:mesh_chj}}
\end{figure}

\subsubsection{Regime I}
In this case, the boundary conditions are given by \eqref{bcs_chj} with
\begin{align}\label{bcs_chj_r1}
  |\bfu_I|=0.75, \qquad h_o=0.37387387318873766. 
\end{align}
The initial condition is a symmetric CHJ located at $\sqrt{x^2+y^2}=0.3$, generated as described in \S \ref{sec:steady_chj}.
In Figure \ref{fig:chj_r1}, we show the magnitude of the momentum at different times using
method \eqref{second-order_via_fluct} with Roe's Riemann solver.
The solution clearly develops carbuncle instabilities.
We could fix these instabilities using Rusanov's, Kemm's or the blended Riemann solvers. 
In Figure \ref{fig:chj_r1_diff}, we show the corresponding solutions at $t=3$.
For this test case, all solvers give qualitatively similar solutions;
however, we expect Rusanov's solver to be less accurate.

\begin{figure}[!h]
  \centering 
  \includegraphics[scale=0.28]{figures/chj_r1_roe_p1.png} \quad
  \includegraphics[scale=0.28]{figures/chj_r1_roe_p2.png} \quad
  \includegraphics[scale=0.28]{figures/chj_r1_roe_p3.png} \quad
  \caption{Magnitude of the momentum for a CHJ with boundary conditions given by
    \eqref{bcs_chj} and \eqref{bcs_chj_r1}. 
    We consider method \eqref{second-order_via_fluct} with Roe's solver.    
    The color scale in the plots go from (blue) $0.0746$ to (red) $0.3738$,
    which corresponds to the minimum and maximum values of the momentum at $t=0$.
    \label{fig:chj_r1}}
\end{figure}

\begin{figure}[!h]
  \centering 
  \includegraphics[scale=0.28]{figures/chj_r1_llf_p3.png} \quad
  \includegraphics[scale=0.5]{figures/cross.png} \quad
  \includegraphics[scale=0.28]{figures/chj_r1_blended_p3.png} \quad
  \caption{Magnitude of the momentum for a CHJ with boundary conditions given by
    \eqref{bcs_chj} and \eqref{bcs_chj_r1}. 
    We consider method \eqref{second-order_via_fluct} with (left) Rusanov's,
    (middle) Kemm's and (right) the blended solvers. 
    The color scale in the plots go from (blue) $0.0746$ to (red) $0.3738$,
    which corresponds to the minimum and maximum values of the momentum at $t=0$.
    \label{fig:chj_r1_diff}}
\end{figure}

\subsubsection{Regime II}
We now consider a more aggresive regime. The boundary conditions are given by \eqref{bcs_chj} with 
\begin{align}\label{bcs_chj_r2}
  |\bfu_I|=15, \qquad h_o=6.6845019298155357.
\end{align}
Similar than before, we follow \S \ref{sec:steady_chj} to generate an initial condition with a symmetric CHJ located at
$\sqrt{x^2+y^2}=0.3$. In Figure XX, we show the magnitude of the momentum at different times using method
\eqref{second-order_via_fluct} with Roe's Riemann solver. Just like before, the solution develops
carbuncle instabilities. Let us now use Rusanov's, Kemm's and the blended solvers to fix the
carbuncle instabilities. In Figure XX, we show the corresponding solutions at $t=XX$.
{\color{red} TODO: finish this part depending on the results with Kemm's solver.}
%
Opposed to what we observed in the first test case, in this situation the Froude number is
high enough that numerical perturbations start to trigger a response around the CHJ.
For the resolution that we consider, this behavior is dissipated by the extra numerical viscosity introduced by
Rusanov's solver. In Figure XX, we show the solution at a later time considering the same solvers as before.
Clearly, using the Rusanov's solver dissipated the physical response to these numerical perturbations.

\begin{figure}[!h]
  \centering 
  \includegraphics[scale=0.28]{figures/chj_r2_roe_p1.png} \quad
  \includegraphics[scale=0.28]{figures/chj_r2_roe_p2.png} \quad
  \includegraphics[scale=0.28]{figures/chj_r2_roe_p3.png}
  \caption{Magnitude of the momentum for a CHJ with boundary conditions given by
    \eqref{bcs_chj} and \eqref{bcs_chj_r2}. 
    We consider method \eqref{second-order_via_fluct} with Roe's solver.
    The color scale in the plots go from (blue) $0.4502$ to (red) $4.4798$,
    which corresponds to the minimum and maximum values of the momentum at $t=0$.
    \label{fig:chj_r2}}
\end{figure}

\begin{figure}[!h]
  \centering 
  \includegraphics[scale=0.28]{figures/chj_r2_llf_t0p1.png} \quad
  \includegraphics[scale=0.5]{figures/cross.png} \quad
  \includegraphics[scale=0.28]{figures/chj_r2_blended_t0p1.png} 
  \caption{Magnitude of the momentum for a CHJ with boundary conditions given by
    \eqref{bcs_chj} and \eqref{bcs_chj_r2}. 
    We consider method \eqref{second-order_via_fluct} with (left) Rusanov's,
    (middle) Kemm's and (right) the blended solvers. 
    The color scale in the plots go from (blue) $0.4502$ to (red) $4.4798$,
    which corresponds to the minimum and maximum values of the momentum at $t=0$.
    \label{fig:chj_r2}}
\end{figure}

\begin{figure}[!h]
  \centering 
  \includegraphics[scale=0.5]{figures/cross.png} \quad
  \includegraphics[scale=0.5]{figures/cross.png} \quad
  \includegraphics[scale=0.28]{figures/chj_r2_blended_t5p0.png} 
  \caption{Magnitude of the momentum for a CHJ with boundary conditions given by
    \eqref{bcs_chj} and \eqref{bcs_chj_r2}. 
    We consider method \eqref{second-order_via_fluct} with (left) Rusanov's,
    (middle) Kemm's and (right) the blended solvers. 
    The color scale in the plots go from (blue) $0.4502$ to (red) $4.4798$,
    which corresponds to the minimum and maximum values of the momentum at $t=0$.
    \label{fig:chj_r2}}
\end{figure}

\subsubsection{Regime II with random perturbations}
Finally, we introduce a physical random perturbation to the inflow boundary condition.
Let $\epsilon(x,y,t)\in[-0.01,0.01]$ be a random number for a given location $(x,y)$,
at a given time $t$. 
The inflow boundary condition is now given by
\begin{subequations}
  \begin{align}
    h(x,y,t)=\tilde h_I, \quad
    u(x,y,t)=|\tilde \bfu_I| \left(\frac{x}{r_I}\right), \quad
    v(x,y,t)=|\tilde \bfu_I| \left(\frac{y}{r_I}\right), \qquad \forall (x,y)\in\partial\Omega_I,
  \end{align}
\end{subequations}
with $\tilde h_I = \frac{h_I}{1+\epsilon(x,y)}$ and $|\tilde\bfu_I|=|\bfu_I|(1+\epsilon(x,y))$.
Here, just as before, $h_I=0.3$ and $|\bfu_I|=15$. 
Note that $\beta=r_I\tilde h|\tilde\bfu_I|=r_Ih_I\bfu_I$.
The outflow boundary condition is given by
\eqref{bcs_chj_outflow} with $h_o=6.6845019298155357$.

\begin{figure}[!h]
  \centering
  \begin{tabular}{cccc}
    \includegraphics[scale=0.24]{figures/chj_r2wp_blended_t1p0.png} &
    \includegraphics[scale=0.24]{figures/chj_r2wp_blended_t2p0.png} &
    \includegraphics[scale=0.24]{figures/chj_r2wp_blended_t4p0.png} &
    \includegraphics[scale=0.24]{figures/chj_r2wp_blended_t6p0.png}
  \end{tabular}
  \caption{XX}
\end{figure}
